### 2011-10-11 doc/theses/mikula/analysis_of_recent_approaches.tex
Master thesis: In progress.

On the contrary, the grammar-inferring methods (\cite{Ahonen1996GeneratingGrammars, Bex:2006:ICD:1182635.1164139, Bex:2007:IXS:1325851.1325964, Hegewald:2006:XES:1129755.1130124, Min:2003:EES:639473.639475}) are based on theoretical knowledge of automata and their results belong to a particular class of languages. Thus, these methods guarantee specific characteristics of the results.

@@

\subsection{Clustering of Elements}
This phase clusters elements on a basis of their context and structure. It is done by creating tree structures for each input XML documents where vertices represent elements and attributes and an edge between two vertices expresses their parent-child relation. These trees are their subtrees and then compared using an imposed tree similarity measure to find elements with the same semantics.

@@

One of the improvements of this heuristic is inclusions of a negative feedback after each step of an ant, visible only in a current iteration. Due to this improvement, a larger subspace of solutions is searched.

Another improvement lies in a way how an ant decides for a particular step to perform. To achieve better results, the authors propose a combinations of several verified approaches. A set of all possible steps is created using \emph{k,h-context} and \emph{s,k-string} \todo{citacie} methods. The optimal step is then selected employing the MDL principle \todo{citacia}.

@@

\section{On Inference of XML Schema with the Knowledge of an Obsolete One}
\todo[inline]{spravne zaradit}
An aim of approach described in \cite{Mlynkova:2009:IXS:1862681.1862693} is to exploit an obsolete XML schema as an additional input information to infer a new schema more efficiently. A XML schema can become obsolete due to changes in a set of XML documents, without capturing these changes in the schema. Thus, the schema becames outdated and according to the paper, this case is quite common.

@@

In the second step, assuming a correct schema it is wanted to specialize the REs involved in the schema with regard to the XML documents, resulting in more precise and readable schema. Optional substeps are pruning of unused schema fragments, correction of lower and upper bounds of occurrences, transcription of operators to a more restrictive but simplier form, if this transcription preserves the validity, and refactorization to improve readability.

@@

\subsection{Join Patterns and Key Inference}
For a certain join, the decision for one of the cases (O1) and (O2) is made by the form of the join. The query is searched for so-called \emph{join patters}. These are \emph{for join pattern} and \emph{let join pattern} and they are as follows (the first is \emph{for join pattern}, \emph{let join pattern}):

@@

Else, the pattern occurrence is considered of case (O2) and the assigned weight depends on the number of target return paths. If the number is greater than one, the weight is one (weight: 1), else (the number is less or equal one) the weight is one half (weight: 0.5).

@@

>>>>

On the contrary, the grammar-inferring methods (\cite{Ahonen1996GeneratingGrammars, Bex:2006:ICD:1182635.1164139, Bex:2007:IXS:1325851.1325964, Hegewald:2006:XES:1129755.1130124, Min:2003:EES:639473.639475, Fernau:2001:LXG:645744.667236}) are based on theoretical knowledge of automata and their results belong to a particular class of languages. Thus, these methods guarantee specific characteristics of the results.

@@

\subsection{Clustering of Elements}
This phase clusters elements on a basis of their context and structure. It is done by creating tree structures for each input XML documents where vertices represent elements and attributes and an edge between two vertices expresses their parent-child relation. These trees and their subtrees are then compared using an imposed tree similarity measure to find elements with the same semantics.

@@

One of the improvements of this heuristic is an inclusion of a negative feedback after each step of an ant, visible only in a current iteration. Due to this improvement, a larger subspace of solutions is searched.

Another improvement lies in a way how an ant decides for a particular step to perform. To achieve better results, the authors propose a combination of several verified approaches. A set of all possible steps is created using \emph{k,h-context} \cite{Ahonen1996GeneratingGrammars} and \emph{s,k-string} \cite{Raman97thesk-strings, Wong03onstructural} methods. The optimal step is then selected employing the MDL principle \cite{Grünwald05atutorial, Garofalakis:2000:XSE:342009.335409}.

@@

\section{On Inference of XML Schema with the Knowledge of an Obsolete One}
An aim of approach described in \cite{Mlynkova:2009:IXS:1862681.1862693} is to exploit an obsolete XML schema as an additional input information to infer a new schema more efficiently. A XML schema can become obsolete due to changes in a set of XML documents, without capturing these changes in the schema. Thus, the schema becames outdated and according to the paper, this case is quite common.

@@

In the second step, assuming a correct schema it is wanted to specialize the regular expressions involved in the schema with regard to the XML documents, resulting in more precise and readable schema. Optional substeps are pruning of unused schema fragments, correction of lower and upper bounds of occurrences, transcription of operators to a more restrictive but simplier form, if this transcription preserves the validity, and refactorization to improve readability.

@@

\subsection{Join Patterns and Key Inference}
For a certain join, the decision for one of the cases (O1) and (O2) is made by the form of the join. The query is searched for so-called \emph{join patters}. These are \emph{for join pattern} and \emph{let join pattern} and they are as follows (the first is \emph{for join pattern}, the latter is \emph{let join pattern}):

@@

Otherwise, the pattern occurrence is considered of case (O2) and the assigned weight depends on the number of target return paths. If the number is greater than one, the weight is one (weight: 1), else (the number equals zero or one) the weight is one half (weight: 0.5).

@@

\section{Summary}
\begin{table}
  \footnotesize \begin{tabular}{|c|c|c|c|c|}
    \hline
    Method name and/or paper & Input & Output & Year & Standalone \\ \hline \hline
    \cite{Ahonen1996GeneratingGrammars} & XML documents & DTD & 1996 & Yes \\ \hline
    XTRACT \cite{Garofalakis:2000:XSE:342009.335409} & XML documents & DTD & 2000 & Yes \\ \hline
    DTD-miner \cite{Moh:2000:RSW:336597.336638} & XML documents & DTD & 2000 & Yes \\ \hline
    \cite{Fernau:2001:LXG:645744.667236} & XML documents & DTD & 2001 & Yes \\ \hline
    ECFG \cite{Chidlovskii:2002:SEX:544220.544288} & XML documents & XSD & 2002 & Yes \\ \hline
    sk-ANT \cite{Wong03onstructural} & XML documents & DTD & 2003 & Yes \\ \hline
    \cite {Min:2003:EES:639473.639475} & XML documents & DTD & 2003 & Yes \\ \hline
    \cite{Bex:2006:ICD:1182635.1164139} & XML documents & DTD & 2006 & Yes \\ \hline
    XStruct \cite {Hegewald:2006:XES:1129755.1130124} & XML documents & XSD & 2006 & Yes \\ \hline
    \cite{Bex:2007:IXS:1325851.1325964} & XML documents & XSD & 2007 & Yes \\ \hline
    SchemaMiner \cite{Vosta:2008:EAC:1802514.1802522} & XML documents & XSD & 2008 & Yes \\ \hline
    \cite{Mlynkova:2009:IXS:1862681.1862693} & XML documents, XML schema & DTD, XSD* & 2009 & Yes \\ \hline
    \cite{Necasky:2009:DXK:1529282.1529414} & XQuery queries & XSD* & 2009 & No \\ \hline    
  \end{tabular}
  \caption{Summary of Recent Approaches}
  \label{table_summary_of_recent_approaches}
\end{table}
